\documentclass[11pt,letterpaper]{article}
\usepackage{geometry}
\usepackage{url}
\usepackage{hanging}
\usepackage{parskip}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage[document]{ragged2e}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{tocloft}
% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
\usepackage{xcolor}
% \usepackage{helvet}
\usepackage{hyperref}
\usepackage{etoolbox}

\newtoggle{resume}
\toggletrue{resume}
%\togglefalse{resume}
\renewcommand{\familydefault}{\sfdefault}

\def\name{Kuya Takami, Ph.D.}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://jblevins.org/projects/cv-template/}
\fancyfoot{}
\fancyhead{}
\fancyfoot[r]{Page \thepage\ of \pageref*{LastPage}}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\headrulewidth}{0.5pt}
% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdfkeywords = {engieering, robotics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
%  body={7in, 9in}
  margin=0.8in,
  left=20mm,
  right=20mm
}

% Customize page headers
\pagestyle{fancy}
\markright{\name}
%\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\large}

\setlength\parindent{0em}

\newcommand{\sect}[1]{\vspace{2mm}{\centering {\bf \large \scshape \uppercase{#1}} \par}  {\color{blue} \vskip 2mm \hrule height 1pt}\vspace{2mm}}

\fancyhead{}% Remove all header contents
% \cfoot{Page \thepage\ of \pageref{LastPage}}% Page X of Y in the footer (centered)
\fancypagestyle{noheader}{%
  \fancyhead{}
  \renewcommand{\headrulewidth}{0pt}
}

\begin{document}

  \thispagestyle{noheader}
  \begin{minipage}{0.7\linewidth}
    % \vspace{-2cm}
  {\vspace{1cm}\fontfamily{qpl}\selectfont \huge {\scshape Kuya Takami}, Ph.D.}\\
  %Email:  \href{mailto:kuya@vt.edu}{\tt kuya@vt.edu} \\
\vspace{5mm}
{\bf Scientific Software Developer} \quad Enthought, Inc.\\
  % Website:  \href{http://www.me.vt.edu/cms/people/kuya-takami}{\tt http://www.me.vt.edu/cms/people/kuya-takami} \\
  %\hspace{4mm}
  GitHub: \href{https://github.com/ku-ya}{\tt https://github.com/ku-ya}\\
  %\hspace{4mm}
  %LinkedIn:  \href{https://www.linkedin.com/in/kuyat}{\tt ttps://www.linkedin.com/in/kuyat} \\

  \end{minipage}
  \hspace{2mm}
  \begin{minipage}{0.6\linewidth}
    \vspace{5mm}
  	Email:  \href{mailto:kuya@gwu.edu}{\tt ktakami@enthought.com} \\
  	Web:  \href{www.kuyatakami.com}{\tt kuyatakami.com} \\
    Phone:  (414)212\-5155\\

  %    Website:  \href{http://www.cmsvt.org/Kuya}{\tt http://www.cmsvt.org/Kuya} \\
    2211 Lawnmont Ave Apt 216\\
    Austin, TX 78756\\
    \vspace{5pt}
    Updated: \today
  \end{minipage}

\vspace{5mm}

\lhead{Kuya Takami}
\rhead{\url{kuyatakami.com}}

\sect{education}
  {\centering
  \begin{minipage}{0.8\columnwidth}
  {\bf Virginia Polytechnic Institute and State University} Blacksburg, VA\\
  \quad Ph.D.,  Mechanical Engineering, 2015   \\
  \qquad {Thesis: ``Non-Field-of-View Acoustic Target Estimation''}\\
  \qquad Advisor: Professor Tomonari Furukawa\\
  % \begin{minipage}{0.45\columnwidth}
  \bigskip
  {\bf University of Wisconsin-Madison} Madison, WI \\
  \hspace{5mm} M.S., Mechanical Engineering, 2011 \\
  \hspace{10mm} Advisor: Professor Scott Sanders\\
  \bigskip
  {\bf University of Wisconsin-Madison} Madison, WI \\
  \hspace{5mm}B.S., Biomedical Engineering (Biomechanics), 2008\\
  \end{minipage}
  \par}

  \sect{Research interests}
  \centerline{Robotics, Perception, Localization and Mapping, Mobile robots}

  % \hrule
  \sect{appointments}
   \MakeUppercase{\bf Enthought, Inc.}\hfill{Austin TX}\\
  \quad {\bf Scientific Software Developer}\hfill {(10/2017 - Present)}\\
  \begin{itemize}
  	\item Development of software used to perform scientific exploration and implementation of scientific advancement including GUI, 2D and 3D graphics, architecture and numerical methods applied to a variety of scientific and engineering problems.
  \end{itemize}
  \MakeUppercase{\bf George Washington University}\hfill{Washington DC}\\
  \quad {\bf Postdoctoral Research Fellow}\hfill {(08/2016 - 10/2017)}\\
  Flight Dynamics and Control Lab with Professor Taeyoung Lee\\
  \begin{itemize}
    \item Conducting research on probabilistic multi-UAV (Unmanned Aerial Vehicle) autonomous exploration and Simultaneous Localization and Mapping.
    \item Developed deep learning based sensor upstream enhancement on mobile robot depth perception.
    \item Creating probabilistic framework based on time dependent sensor fusion.
  \end{itemize}
  \MakeUppercase{\bf Virginia Tech}\hfill{Blacksburg, VA }\\
  \quad {\bf Postdoctoral Research Fellow}\hfill {(10/2015 - 07/2016)}\\
  Computational Multiphysics and Systems Lab with Professor Tomonari Furuakwa\\

  \begin{itemize}
  	\item Primary researcher on National Science Foundation EAGER project, non-line-of-sight (NLOS) target localization in an unknown environment.
  	\begin{itemize}
  		\item Developed probabilistic approach to NLOS visual/ acoustical target estimation based on recursive Bayesian estimation framework, and conducting test on human/ mobile sensor platform for human-robot-interaction.
  		\item Collaboration with Daniel Kish, president of World Access for the Blind, for perception of acoustic diffraction and reflection signal processing for human echolocation experts.
  		\item Grant proposal writing for National Robotics Initiative (NRI) NSF16-517 with Dr. Furukawa.
  	\end{itemize}
  	\item Leader of Mohamed Bin Zayed International Robotics Challenge 2017 mobile manipulator team for the Challenge 2. The project consists of perception, navigation, and manipulation based on actual mobile robots to operate the valve with tools.
  	\item Developed and implemented an FPGA based high-resolution imaging system with the integration to tire testing machine at Toyo Rubber.
  	\item Developing an autonomous car and associative technologies including new sensors for a project sponsored by General Motors and Murata Manufacturing. \item Advising one MS student for the NSF EAGER project and mentoring a senior design project, Self-Driving Vehicle Team, consisting of nine senior students.
  \end{itemize}

  %\MakeUppercase{\bf Virginia Polytecnic Institute and State University}\hfill{Blacksburg, VA }
  \quad {\bf Graduate Research Assistant/ *Graduate Teaching Assistant}\hfill {(08/2011 - 09/2015)}\\
  \begin{itemize}
  \item Developed NLOS hybrid optical/acoustical target localization scheme to model and predict the state of sound source in a complex environment (2011-2015).
  \item Modeled sound reflection/diffraction based NLOS target estimation for mobile robot localization (2011-2015).
  \item Assisted underwater autonomous navigation project on sonar localization simulation using simultaneous localization and mapping (SLAM) funded by Office of Naval Research (2011-2012).
  \item Worked on real-time autonomous driving using Grid-based SLAM in collaboration with ZMP and University of Technology, Sydney (2012-2014).
  \item Worked on tire noise prediction model entailing mathematical formulations, and fluid-solid interaction modeling funded by NSF Center for Tire Research (2012-2015).
  \end{itemize}

  \MakeUppercase{\bf Bridgestone Americas, Inc}\hfill{Akron, OH}{ (05 - 08/2014)}\\
  \quad {\bf Advanced Tire Technology - Research intern}\\
  \begin{itemize}
  \item Developed tire noise analysis procedure and designed and implemented tire noise experimental device based on an FPGA controller.
  \end{itemize}

  \MakeUppercase{\bf ZMP, Inc}\hfill{Tokyo, Japan }{(01 - 07/2013)}\\
  \quad {\bf Research Engineer in Autonomous Vehicles}
  \begin{itemize}
  \item Assisted programming and hardware development for an autonomous driving vehicle, including data acquisition, implementation of SLAM, and vehicle modeling/control.
  \item Designed and constructed a quadrupedal machine learning-based evolving robot by calculating kinematics and specifying components.
  \end{itemize}

  \MakeUppercase{\bf University of Wisconsin-Madison}\hfill{Madison, WI}{ (03/2009 - 08/2011)}\\
  \quad {\bf Graduate Research Assistant for Engine Research Center}
  \begin{itemize}
  \item Conducted laser and fiber optics centered research optimizing optical element design in harsh environments.
  \item Developed a noninvasive laser grid tomography temperature measurement system for jet and IC engines.
  \end{itemize}

  \MakeUppercase{\bf University of Wisconsin Hospital}\hfill{Madison, WI}{ {(08/2007 - 12/2008)}}\\
  \quad {\bf MRI Research Assistant for Radiology Department}
  \begin{itemize}
  \item Studied MRI-based knee analysis, quantified quality of the image, and determined change of cartilage volumes.
  \end{itemize}

\sect{Selected Journal Papers}
  \begin{enumerate}
  \item E. Kaufman, {\bf K. Takami}, T. Lee, Z. Ai. ``Autonomous Exploration with Exact Inverse Sensor Models,'' Springer Journal of Intelligent \& Robotic Systems, (March 2017 Accepted)

  \item {\bf K. Takami}, L. Hangxin, T. Furukawa, M. Kumon, G. Dissanayake. ``Reflection and Diffraction Signals based Recursive Bayesian Estimation for Non-Field-of-View Target,'' (in preparation).

  \item {\bf K. Takami}, T. Furukawa. ``Development of a High-Resolution Measurement System for Rotating Deformable Body,'' Journal of Visualization (under review).

  \item {\bf K. Takami}, T. Furukawa, M. Kumon, D. Kimoto, and G. Dissanayake. ``Estimation of a Nonvisible Field-of-View Mobile Target Incorporating Optical and Acoustic Sensors,'' Autonomous Robots, 2015.

  \item {\bf K. Takami}, T. Furukawa, M. Kumon, and G. Dissanayake. ``Non-Field-of-View Acoustic Target Estimation in Complex Indoor Environment,'' Springer Tracts in Advanced Robotics, 2015.

  \item J. M. Whitney, {\bf K. Takami}, S. T. Sanders, and Y. Okura. ``Design of system for rugged, low-noise fiber-optic access to high-temperature, high-pressure environments,'' Sensors Journal, IEEE, 2011.

  \item A. Xinliang, T. Kraetschmer, {\bf K. Takami}, S. T. Sanders, L. Ma, et al. ``Validation of temperature imaging by H$_2$O absorption spectroscopy using hyperspectral tomography in controlled experiments,'' Journal of Applied Optics, 2011.
\end{enumerate}

\sect{Selected Conference papers and workshop}
\begin{enumerate}
	\item {\bf K. Takami}, T. Lee, ``Environment dependent depth enhancement with multi-modal sensor fusion learning,'' IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), 2017 (Submitted)
	\item {\bf K. Takami}, H. Liu, T. Furukawa, M. Kumon, and G. Dissanayake, ``Non-Field-of-View Sound Source Localization	Using Diffraction and Reflection Signals,'' IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), 2016
  \item {\bf K. Takami}, H. Liu, T. Furukawa, M. Kumon, and G. Dissanayake, ``Recursive Bayesian Estimation of NFOV Target Using Diffraction and Reflection Signals,'' ISIF International Conference on Information Fusion, 2016
  \item  {\bf K. Takami}, T. Furukawa, M. Kumon, and L. Mak,``Non-Field-of-View Indoor Sound Source Localization based on Reflection and Diffraction,'' Multi-sensor Integration and Fusion, IEEE, 2015.
  \item {\bf K. Takami}, T. Furukawa, M. Kumon, and G. Dissanayake. ``Non-Field-of-View Acoustic Target Estimation in Complex Indoor Environment,'' Field and Service Robotics, 2015.
  \item  T. Furukawa, {\bf K. Takami}, X. Tong, D. Watman, A. Hamed, R. Ranasinghe and G. Dissayanake, ``Map-based Navigation of an Autonomous Car Using Grid-based Scan-to-Map Matching,'' ASME IDETC, 2015.
  \item  {\bf K. Takami} and T. Furukawa,``High-Resolution Deformation Measurement System for Fast Rotating Tire\,'' ASME IDETC/CIE, 2015.


  \item  {\bf K. Takami} and T. Furukawa,``High-Resolution Deformation Measurement System for Fast Rotating Tires Towards Noise Prediction,'' Euronoise., 2015.
  \iftoggle{resume}{}{
  \item M. Kumon, D. Kimoto, {\bf K. Takami} and T. Furukawa, ``Acoustic recursive Bayesian estimation for non-field-of-view targets,'' In Image Analysis for Multimedia Interactive Services (WIAMIS), IEEE, 2013.
}
  \item M. Kumon, D. Kimoto, {\bf K. Takami} and T. Furukawa. ``Bayesian non-field-of-view target estimation incorporating an acoustic sensor,'' IEEE/RSJ International Conference on Intelligent Robots and Systems  (IROS), 2013.
  \iftoggle{resume}{}{

  \item {\bf K. Takami}, S. Taheri, M. Taheri and T. Furukawa, ``Prediction of Railroad Track Foundation Defects Using Wavelets,'' Joint Rail Conference, ASME, 2013.
  }
\end{enumerate}

  % \vspace{-5mm}
  % \section*{HONORS AND AWARDS}\vspace{-3mm}
  % \hrule

  \sect{honors and awards}
  \hspace{0mm}
  \begin{minipage}{\columnwidth}
  \begin{minipage}{0.5\columnwidth}
  \begin{tabular}{l l}
  2007 & Most Outstanding Physics Award$^\dagger$ \\
  2012 & Pratt Graduate Fellowship$^\ddagger$\\
  2015 & ASME:IDETC/CIE Best Student Paper Award\\
  \end{tabular}
  \end{minipage}
  \hfill
  \begin{minipage}{0.4\columnwidth}
  \begin{tabular}{l l}
  2011 & Pratt Graduate Fellowship$^\ddagger$ \\
  2014 & Pratt Graduate Fellowship$^\ddagger$\\
  \end{tabular}
  \end{minipage}

  \vspace{5mm}
  $\dagger$: Scholarship to the best student in two semester physics courses at University of Wisconsin-EC\\
  $\ddagger$: Awarded to students who are aggressively recruited by other top engineering colleges\\
  \end{minipage}

\iftoggle{resume}{}
{
  % \section*{TECHNICAL STRENGTH}\vspace{-3mm}
  % \hrule


  % \section*{EXTRACURRICULAR EXPERIENCE}\vspace{-3mm}
  %
  % \hrule


  % \section*{PUBLICATIONS}\vspace{-3mm}
  % \hrule

\sect{invited talks and guest lectures}
\begin{itemize}
  \item ``High-Resolution Deformation Measurement System for Fast Rotating Tires Towards Noise Prediction'' speaker at Apollo Tyres Global R\&D, Netherland, Mar. 2015
  \item ``High-Resolution Deformation Measurement System for Fast Rotating Tires Towards Noise Prediction'' speaker at Applied Mechanics at Twente University, Netherland, Mar. 2015
  \item ``Visualization system for Tire rolling rig'', speaker at Bridgestone, Aug. 2014
\end{itemize}


\sect{miscellaneous}
{\bf Grant proposal}:\\
\begin{itemize}
  \item NSF National Robotics Initiative (Pending): Participated as a grant writer
  \item NSF 1554961 (Granted \$165k): Reflection and Diffraction Sound Signals for Non-Field-of-View Target Estimation, Participated as a grant writer
  \item MURATA (Granted \$265k): Contributed to technical development
\end{itemize}
{\bf Service to the field}:\\
Reviewer: ASME Journal of Vibration and Acoustics, IEEE IROS

{\bf Mentoring}:\\
Hangxin Liu: Virginia Tech Undergraduate - beginning MS at UCLA\\
Alex Giratd: Virginia Tech MS\\
Yung Wang: Virginia Tech Undergraduate\\

\begin{itemize}
\item {\bf Instructor} (ME 2024-Engineering Design and Economics): Lectured mechanical engineering students on product development (Fall 2013).
\item {\bf Project Advisor } (ME4015/4016): Supervised senior design project on autonomous driving, and automotive alternator design and experimental validation (2011-2012).
\end{itemize}
}
%\item *Laboratory Assistant (ME4005/4006): Instructed and organized junior/ senior mechanical engineering labs and graded technical reports.

 \sect{technical strength}
   \begin{minipage}{0.58\columnwidth}
   \begin{tabular}{ll}
   Computer Languages:& C/C++ (8/10), Python (7/10)\\
   Software:& ROS, MATLAB \\
   CAD:& SolidWorks, PTC Creo\\
   \end{tabular}
   \end{minipage}
   \begin{minipage}{0.35\columnwidth}
   \begin{tabular}{ll}
   System: & Windows, Linux, OS X\\
   Languages: & English, Japanese (native)\\
   \end{tabular}
   \end{minipage}


\iftoggle{resume}{}{
 \sect{extracurricular experience}
 \begin{minipage}{\columnwidth}
 \begin{tabular}{ l  l }
   Organization & Mechanical Engineering Graduate Student Council (2013-2015)\\
   & Mechanical Engineering Graduate Ambassador (2013-2015)\\
   & President of VT Slackline Club (2011-2014)\\
   & President of Japanese Conversation Group (2012-2015)\\
   & President of Japanese Cultural Society in University of Wisconsin-EC (2005-2006)\\
   Volunteer & Graduate student mentor (2014-Present)\\
   Society & National Society of Leadership and Success, Biomedical Engineering Society
 \end{tabular}
 \end{minipage}



\sect{References}
\begin{itemize}
  \item Dr. Tomonari Furukawa\\
  Professor\\Department of Mechanical Engineering, Virginia Tech\\
  Email: tomonari@vt.edu\\
  \item Dr. Robert Parker\\Professor\\Department of Mechanical Engineering, Virginia Tech\\
  Email: r.parker@vt.edu
  \item Dr. Scott Sanders\\Professor\\Department of Mechanical Engineering, University of Wisconsin-Madison\\
  Email: stsanders@wisc.edu
\end{itemize}
}
  %\fancyfoot{
  %\begin{center}
  %  \begin{footnotesize}
  %    Last updated: \today \\
  %  \end{footnotesize}
  %\end{center}
  %}

\end{document}
