\documentclass[11pt,letter]{article}
%	options include 12pt or 11pt or 10pt
%	classes include article, report, book, letter, thesis
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{geometry}
\usepackage{tocloft}
\usepackage[colorlinks=false,linkcolor=black,hidelinks]{hyperref}
\geometry{
%	a4paper,
%	total={170mm,257mm},
	left=20mm,
	right = 20mm,
	top=20mm,
	bottom = 20mm,
}
\fancyhf{} % sets both header and footer to nothing
\renewcommand{\headrulewidth}{0pt}
\fancyfoot{}
\fancyhead{}
\fancyfoot[C]{Kuya Takami -- Page \thepage\ of \pageref{LastPage} -- Resume}
\pagestyle{fancy}
\newcommand{\job}[6]{
	\begin{tabbing}
		\hspace{2cm} \= \kill
		\textbf{#1} \> \href{#4}{#3} \\
		\textbf{#2} \>\+ \textit{#5} \\
		\begin{minipage}{\smallertextwidth}
			\vspace{2mm}
			#6
		\end{minipage}
	\end{tabbing}
	\vspace{2mm}
}

\begin{document}
{\bf \huge \noindent Kuya Takami Ph.D.}\vspace{-2mm}\\
\rule{\textwidth}{1.7pt}

\parbox{0.4\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
		\hspace{0.5cm} \= \kill % Spacing within the block
		\> Digital Transformation Services Consultant\\
		\> Enthought Inc.
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.4\textwidth}{ % Second block
	\begin{tabbing} % Enables tabbing
		\hspace{1cm} \= \hspace{4cm} \= \kill % Spacing within the block
		\> Updated: \today \\ % Home phone
		\> Email:\href{mailto:kuya@vt.edu}{\tt kuya@vt.edu}  \\ % Mobile phone
	\end{tabbing}
}\\
\parbox{0.7\textwidth}{
\begin{tabbing}
	\hspace{1cm} \= \kill
	\>	{\bf \MakeUppercase{Research Interests}}\\
	\>	Robot Audition, Human-Robot Interaction, Mobile Robot, Bayesian Robotics
\end{tabbing}
}
\\
\vspace{-2mm}
\begin{tabbing}
	\hspace{1cm}\=\kill
	\>  {\bf \Large EDUCATION}
\end{tabbing} \vspace{-7mm}
\begin{tabbing}
	\hspace{3cm} \= \kill
	{\footnotesize } \> {\bf Virginia Tech}, Blacksburg, VA\\
	\> \quad  Ph.D.  Mechanical Engineering, 2015 \\
	\> \quad Dissertation: {\it Non-Field-of-View Acoustic Target Estimation}\\
	\> \quad Advisor: Professor Tomonari Furukawa
\end{tabbing}
\begin{tabbing}
	\hspace{3cm} \= \kill
	{\footnotesize } \> {\bf University of Wisconsin-Madison}, Madison, WI\\
	\> \quad M.S.  Mechanical Engineering, 2011 \\
	\> \quad Advisor: Professor Scott Sanders
\end{tabbing}
\begin{tabbing}
	\hspace{3cm} \= \kill
	{\footnotesize } \> {\bf University of Wisconsin-Madison}, Madison, WI\\
	\> \quad B.S.  Biomedical Engineering (Biomecanics), 2008\\
\end{tabbing}


\begin{tabbing}
	\hspace{1cm}\=\kill
	\>  {\bf \Large APPOINTSMENTS}
\end{tabbing}\vspace{-7mm}
\begin{tabbing}
	\hspace{3cm} \= \kill
	10/2015 - Present \> {\bf Virginia Polytecnic Institute and State University}\hfill{Blacksburg, VA }\\
	\> {\bfseries Postdoctoral Research Fellow}	Computational Multiphysics and Systems Lab\\
	\> Professor Tomonari Furuakawa\\
\end{tabbing}
\vspace{-1cm}
%	\begin{minipage}{0.9\textwidth}
			\begin{itemize}
				\item Primary researcher on National Science Foundation EAGER project, non-line-of-sight (NLOS) target localization in an unknown environment.
				\begin{itemize}
					\item Developed probabilistic approach to NLOS visual/ acoustical target estimation based on recursive Bayesian estimation framework, and conducting test on human/ mobile sensor platform for human-robot-interaction.
					\item Collaboration with Daniel Kish, president of World Access for the Blind, for perception of acoustic diffraction and reflection signal processing for human echolocation experts.
					\item Grant proposal writing for National Robotics Initiative (NRI) NSF16-517 with Dr. Furukawa.
				\end{itemize}
				\item Leader of Mohamed Bin Zayed International Robotics Challenge 2017 team for the Challenges. The project consists of perception, navigation, and manipulation based on actual mobile robots to operate the valve with tools.
%				\item Developed and implemented an FPGA based high-resolution imaging system with the integration to tire testing machine.
				\item Developing an autonomous car and associative technologies including new sensors for a project sponsored by General Motors and Murata Manufacturing. Advising one MS student for the NSF EAGER project and mentoring a senior design project, Self-Driving Vehicle Team, consisting of nine senior students.
			\end{itemize}
%	\end{minipage}
%\end{tabbing}

\begin{tabbing}
	\hspace{3cm} \= \kill
	08/2011 - 09/2015 \> VT {\bf Graduate Research Assistant/ *Graduate Teaching Assistant}\\
	\>\hspace{-2cm}\begin{minipage}{0.9\textwidth}
		\begin{itemize}
			\item Developed NLOS hybrid optical/acoustical target localization scheme to model and predict the state of sound source in a complex environment (2011-2015).
			\item Modeled sound reflection/diffraction based NLOS target estimation for mobile robot localization (2011-2015).
			\item Assisted underwater autonomous navigation project on sonar localization simulation using simultaneous localization and mapping (SLAM) funded by Office of Naval Research (2011-2012).
			\item Worked on real-time autonomous driving using Grid-based SLAM in collaboration with ZMP and University of Technology, Sydney (2012-2014).
			\item Worked on tire noise prediction model entailing mathematical formulations, and fluid-solid interaction modeling funded by NSF Center for Tire Research (2012-2015).
%			\item *Instructor (ME 2024-Engineering Design and Economics): Lectured mechanical engineering students on product development (Fall 2013).
			%\item *Laboratory Assistant (ME4005/4006): Instructed and organized junior/ senior mechanical engineering labs and graded technical reports.
			\item *Project Advisor (ME4015/4016): Supervised senior design project on autonomous driving, and automotive alternator design and experimental validation (2011-2012).
		\end{itemize}
	\end{minipage}
\end{tabbing}

\begin{tabbing}
	\hspace{3.5cm} \= \kill
	05/2014 -- 08/2014 \> {\bf Bridgestone Americas, Inc}\hfill{Akron, OH}\\
	\> {\bf Advanced Tire Technology - Research intern}\\
	\> \hspace{-2.5cm}\begin{minipage}{0.9\textwidth}
		\begin{itemize}
			\item Developed tire noise analysis procedure and designed and implemented tire noise experimental device based on an FPGA controller.
		\end{itemize}
	\end{minipage}
\end{tabbing}
\begin{tabbing}
	\hspace{3.5cm} \= \kill
	01/2013 - 07/2013 \> {\bf ZMP, Inc}\hfill{Tokyo, Japan }\\
	\> {\bf Research Engineer in Autonomous Vehicles}\\
	\> \hspace{-2.5cm} \begin{minipage}{0.9\textwidth}
		\begin{itemize}
			\item Assisted programming and hardware development for an autonomous driving vehicle, including data acquisition, implementation of SLAM, and vehicle modeling/control.
			\item Designed and constructed a quadrupedal machine learning-based evolving robot by calculating kinematics and specifying components.
		\end{itemize}
	\end{minipage}
\end{tabbing}
\begin{tabbing}
	\hspace{3.5cm} \= \kill
	 03/2009 - 08/2011 \>{\bf University of Wisconsin-Madison}\hfill{Madison, WI}{ (03/2009 - 08/2011)}\\
	 \> {\bf Graduate Research Assistant for Engine Research Center}\\
	 \> \hspace{-2.5cm}\begin{minipage}{0.9\textwidth}
	 	\begin{itemize}
	 		\item Conducted laser and fiber optics centered research optimizing optical element design in harsh environments.
	 		\item Developed a noninvasive laser grid tomography temperature measurement system for jet and IC engines.
	 	\end{itemize}
	 \end{minipage}
\end{tabbing}
%\begin{tabbing}
%	\hspace{3.5cm} \= \kill
%	05/2014 -- 08/2014 \> {\bf University of Wisconsin Hospital}\hfill{Madison, WI}{ {(08/2007 - 12/2008)}}\\
%	\> {\bf MRI Research Assistant for Radiology Department}\\
%	\> 	\hspace{-2cm}\begin{minipage}{0.9\textwidth}Studied MRI-based knee analysis, quantified quality of the image, and determined change of cartilage volumes.
%	\end{minipage}
%\end{tabbing}


%\begin{tabbing}
%	\hspace{3cm}\=\kill
%	\>  {\bf peer reviewed publications}
%\end{tabbing}
%
%\begin{tabbing}
%	\hspace{3cm}\=\kill
%	\>  {\bf teaching}
%\end{tabbing}

%\section*{TECHNICAL STRENGTH}\vspace{-3mm}
\rhead{Takami-Resume}
	\begin{tabbing}
		\hspace{1cm}\=\kill
		\>  {\bf \Large TECHNICAL STRENGTH}
	\end{tabbing}\vspace{-7mm}
\begin{tabbing}
	\hspace{0cm} \= \kill
	\> \begin{minipage}{0.56\columnwidth}
		\begin{tabular}{ll}
			Computer Languages:& C/C++, Java\\
			Software:& ROS, MATLAB, Visual Studio \\
			CAD \& FEA:& SolidWorks, PTC Creo, Abaqus\\
		\end{tabular}
	\end{minipage}
	\begin{minipage}{0.34\columnwidth}
		\begin{tabular}{ll}
			System: & Windows, Linux, OS X\\
			Languages: & English, Japanese (native)\\
		\end{tabular}
	\end{minipage}
\end{tabbing}

\begin{tabbing}
	\hspace{1cm}\=\kill
	\>  {\bf \Large AWARDS AND HONORS}
\end{tabbing}\vspace{-7mm}
\begin{tabbing}
	\hspace{1cm} \= \kill
	2015 \> ASME:IDETC/CIE Best Student Paper Award\\
	2014 \> Pratt Graduate Fellowship$\ddagger$\\
	2012 \> Pratt Graduate Fellowship$\ddagger$\\
	2011 \> Pratt Graduate Fellowship$\ddagger$\\
	2007 \> Most Outstanding Physics Award$\dagger$\\
	\> 	$\ddagger$: Awarded to students who are aggressively recruited by other top engineering colleges\\
	 \> $\dagger$: Scholarship to the best student in physics courses at University of Wisconsin-EC\\
\end{tabbing}

\begin{tabbing}
	\hspace{1cm}\=\kill
	\>  {\bf \Large EXTRACURRICULAR EXPERIENCE}
\end{tabbing}\vspace{-7mm}
%\section*{EXTRACURRICULAR EXPERIENCE}\vspace{-3mm}
\begin{tabbing}
	\hspace{3cm} \= \kill
	2013 -- 2015 \> Mechanical Engineering Graduate Student Council\\
	2013 -- 2015 \> Mechanical Engineering Graduate Ambassador\\
	2011 -- 2014 \> President of VT Slackline Club\\
	2012 -- 2015 \>	 President of Japanese Conversation Group\\
	2005 -- 2006\>	 President of Japanese Cultural Society in University of Wisconsin-EC\\
	2014 -- 2015 \> Volunteer  Graduate student mentor\\
	\> Society National Society of Leadership and Success, Biomedical Engineering Society
\end{tabbing}

%\section*{PUBLICATIONS}

\begin{tabbing}
	\hspace{1cm}\=\kill
	\>  {\bf \Large PUBLICATIONS}
\end{tabbing}\vspace{-2mm}
\vspace{-1.2cm}
\begin{tabbing}
\end{tabbing}
\begin{itemize}[leftmargin=*]
		\item {\bf K. Takami}, T. Furukawa, M. Kumon, D. Kimoto, and G. Dissanayake. ``Estimation of a nonvisible field-of-view mobile target incorporating optical and acoustic sensors,'' Autonomous Robots, 2015.
	\item {\bf K. Takami}, T. Furukawa, M. Kumon, and G. Dissanayake. ``Non-Field-of-View Acoustic Target Estimation in Complex Indoor Environment,'' Springer Tracts in Advanced Robotics, 2015.
	\item  {\bf K. Takami}, T. Furukawa, M. Kumon, and L. Mak,``Non-Field-of-View Indoor Sound Source Localization based on Reflection and Diffraction,'' Multi-sensor Integration and Fusion, IEEE, 2015.
	\item {\bf K. Takami}, T. Furukawa, M. Kumon, and G. Dissanayake. ``Non-Field-of-View Acoustic Target Estimation in Complex Indoor Environment,'' Field and Service Robotics, 2015.
	\item  T. Furukawa, {\bf K. Takami}, X. Tong, D. Watman, A. Hamed, R. Ranasinghe and G. Dissayanake, ``Map-based Navigation of an Autonomous Car Using Grid-based Scan-to-Map Matching,'' ASME IDETC, 2015.
	\item  {\bf K. Takami} and T. Furukawa,``High-Resolution Deformation Measurement System for Fast Rotating Tire,'' ASME IDETC/CIE, 2015.
	\item  {\bf K. Takami} and T. Furukawa,``High-Resolution Deformation Measurement System for Fast Rotating Tires Towards Noise Prediction,'' Euronoise., 2015.
	\item M. Kumon, D. Kimoto, {\bf K. Takami} and T. Furukawa, ``Acoustic recursive Bayesian estimation for non-field-of-view targets,'' In Image Analysis for Multimedia Interactive Services (WIAMIS), IEEE, 2013.
	\item M. Kumon, D. Kimoto, {\bf K. Takami} and T. Furukawa. ``Bayesian non-field-of-view target estimation incorporating an acoustic sensor,'' In Intelligent Robots and Systems, IEEE/RSJ International Conference, 2013.
	\item {\bf K. Takami}, S. Taheri, M. Taheri and T. Furukawa, ``Prediction of Railroad Track Foundation Defects Using Wavelets,'' Joint Rail Conference, ASME, 2013.
	\item J. M. Whitney, {\bf K. Takami}, S. T. Sanders, and Y. Okura. ``Design of system for rugged, low-noise fiber-optic access to high-temperature, high-pressure environments,'' Sensors Journal, IEEE, 2011.
	\item A. Xinliang, T. Kraetschmer, {\bf K. Takami}, S. T. Sanders, L. Ma, et al. ``Validation of temperature imaging by H$_2$O absorption spectroscopy using hyperspectral tomography in controlled experiments,'' Journal of Applied Optics, 2011.
\end{itemize}
\end{document}
